Reanalysis Step 8: Patient-Level Table 1

### 2025-09-05 reanalysis-8-table1.qmd
table1 refactor

    # Original
    orig_row <- original[original$variable == v, ]
    if (nrow(orig_row) > 0 && !is.na(orig_row$mean)) {
      table_df$Original[i] <- sprintf("%.2f (%.2f)", orig_row$mean, orig_row$sd)
    }

    # Submitted
    sub_row <- submitted[submitted$variable == v, ]
    if (nrow(sub_row) > 0 && !is.na(sub_row$mean)) {
      table_df$Submitted[i] <- sprintf("%.2f (%.2f)", sub_row$mean, sub_row$sd)
    }

    # Excluded
    exc_row <- excluded[excluded$variable == v, ]
    if (nrow(exc_row) > 0 && !is.na(exc_row$mean)) {
      table_df$Excluded[i] <- sprintf("%.2f (%.2f)", exc_row$mean, exc_row$sd)
    }

    # Imputed
    imp_row <- imputed[imputed$variable == v, ]
    if (nrow(imp_row) > 0 && !is.na(imp_row$mean)) {
      table_df$Imputed[i] <- sprintf("%.2f (%.2f)", imp_row$mean, imp_row$sd)
    }
  }

@@

    # Original
    orig_row <- original[original$variable_std == v, ]
    if (nrow(orig_row) > 0 && !is.na(orig_row$n)) {
      table_df$Original[i] <- sprintf("%.0f (%.1f%%)", orig_row$n, orig_row$pct)
    }

    # Submitted
    sub_row <- submitted[submitted$variable_std == v, ]
    if (nrow(sub_row) > 0 && !is.na(sub_row$n)) {
      table_df$Submitted[i] <- sprintf("%.0f (%.1f%%)", sub_row$n, sub_row$pct)
    }

    # Excluded
    exc_row <- excluded[excluded$variable_std == v, ]
    if (nrow(exc_row) > 0 && !is.na(exc_row$n)) {
      table_df$Excluded[i] <- sprintf("%.0f (%.1f%%)", exc_row$n, exc_row$pct)
    }

    # Imputed
    imp_row <- imputed[imputed$variable_std == v, ]
    if (nrow(imp_row) > 0 && !is.na(imp_row$n)) {
      table_df$Imputed[i] <- sprintf("%.1f (%.1f%%)", imp_row$n, imp_row$pct)
    }
  }

@@

# Display continuous variables
kable(continuous_table, 
      caption = "Continuous Variables: Mean (SD)",
      col.names = c("Variable", "Original", "Submitted", "Excluded", "Imputed (Average)"))

# Display categorical variables
kable(categorical_table,
      caption = "Categorical Variables: N (%)",
      col.names = c("Variable", "Original", "Submitted", "Excluded", "Imputed (Average)"))

@@

kable(sample_sizes, caption = "Sample Sizes")
```

@@

```{r stratified-complete-cases}
# Use submitted_data for complete cases analysis
complete_cases_data <- submitted_data

@@

# Function to calculate stratified statistics
calculate_stratified_stats <- function(data, var, is_continuous = FALSE) {
  if (is_continuous) {
    # For continuous variables, calculate mean ± SD
    stats <- data |>
      group_by(lapse_group) |>
      summarise(
        mean = mean(!!sym(var), na.rm = TRUE),
        sd = sd(!!sym(var), na.rm = TRUE),
        .groups = "drop"
      ) |>
      mutate(
        stat = sprintf("%.2f ± %.2f", mean, sd)
      )

    # Add total
    total_stat <- data |>
      summarise(
        mean = mean(!!sym(var), na.rm = TRUE),
        sd = sd(!!sym(var), na.rm = TRUE)
      ) |>
      mutate(
        lapse_group = "Total",
        stat = sprintf("%.2f ± %.2f", mean, sd)
      )

@@

  } else {
    # For categorical variables
    # Calculate counts within each lapse group
    lapse_stats <- data |>
      filter(lapse_group == "Lapse in care") |>
      count(!!sym(var)) |>
      mutate(
        total_lapse = sum(n),
        pct = 100 * n / total_lapse,
        stat_lapse = sprintf("%d (%.0f%%)", n, pct)
      ) |>
      rename(level = !!sym(var))

    no_lapse_stats <- data |>
      filter(lapse_group == "No lapse in care") |>
      count(!!sym(var)) |>
      mutate(
        total_no_lapse = sum(n),
        pct = 100 * n / total_no_lapse,
        stat_no_lapse = sprintf("%d (%.0f%%)", n, pct)
      ) |>
      rename(level = !!sym(var))

    # Calculate total
    total_stats <- data |>
      count(!!sym(var)) |>
      mutate(
        total_all = sum(n),
        pct = 100 * n / total_all,
        stat_total = sprintf("%d (%.0f%%)", n, pct)
      ) |>
      rename(level = !!sym(var))

@@

  # Total row
  results$Total <- data.frame(
    Variable = "Total",
    Lapse = sprintf("%d (%.0f%%)", n_lapse, 100*n_lapse/n_total),
    NoLapse = sprintf("%d (%.0f%%)", n_no_lapse, 100*n_no_lapse/n_total),
    Total = sprintf("%d (100%%)", n_total),
    stringsAsFactors = FALSE
  )

@@

  # Display totals
  cat("**Total Patients**\n")
  knitr::kable(table_data$totals)

@@

  cat("\n*Sex*\n")
  knitr::kable(table_data$sex)

  cat("\n*Age (years)*\n")
  knitr::kable(table_data$age)

  cat("\n*Race/Ethnicity*\n")
  knitr::kable(table_data$race)

  cat("\n*Insurance*\n")
  knitr::kable(table_data$insurance)

@@

  cat("\n*Severity of DR*\n")
  knitr::kable(table_data$dr)

  cat("\n*DR Treatments (% with treatment)*\n")
  treatments_df <- data.frame(
    Treatment = c("PRP", "Focal laser", "Anti-VEGF", "Other injections"),
    Lapse = c(
      sprintf("%d (%.0f%%)", table_data$treatments$prp$n[1], table_data$treatments$prp$pct[1]),
      sprintf("%d (%.0f%%)", table_data$treatments$focal$n[1], table_data$treatments$focal$pct[1]),
      sprintf("%d (%.0f%%)", table_data$treatments$vegf$n[1], table_data$treatments$vegf$pct[1]),
      sprintf("%d (%.0f%%)", table_data$treatments$other$n[1], table_data$treatments$other$pct[1])
    ),
    NoLapse = c(
      sprintf("%d (%.0f%%)", table_data$treatments$prp$n[2], table_data$treatments$prp$pct[2]),
      sprintf("%d (%.0f%%)", table_data$treatments$focal$n[2], table_data$treatments$focal$pct[2]),
      sprintf("%d (%.0f%%)", table_data$treatments$vegf$n[2], table_data$treatments$vegf$pct[2]),
      sprintf("%d (%.0f%%)", table_data$treatments$other$n[2], table_data$treatments$other$pct[2])
    ),
    Total = c(
      sprintf("%d (%.0f%%)", table_data$treatments$prp$n[3], table_data$treatments$prp$pct[3]),
      sprintf("%d (%.0f%%)", table_data$treatments$focal$n[3], table_data$treatments$focal$pct[3]),
      sprintf("%d (%.0f%%)", table_data$treatments$vegf$n[3], table_data$treatments$vegf$pct[3]),
      sprintf("%d (%.0f%%)", table_data$treatments$other$n[3], table_data$treatments$other$pct[3])
    )
  )
  knitr::kable(treatments_df, col.names = c("Treatment", "Lapse in care", "No lapse in care", "Total"))

  cat("\n*Ophthalmologic Comorbidities*\n")
  comorb_df <- data.frame(
    Condition = c("Glaucoma", "Prior cataract surgery", "Other retinal disease"),
    Lapse = c(
      sprintf("%d (%.0f%%)", table_data$comorbidities$glaucoma$n[1], table_data$comorbidities$glaucoma$pct[1]),
      sprintf("%d (%.0f%%)", table_data$comorbidities$cataract$n[1], table_data$comorbidities$cataract$pct[1]),
      sprintf("%d (%.0f%%)", table_data$comorbidities$retina$n[1], table_data$comorbidities$retina$pct[1])
    ),
    NoLapse = c(
      sprintf("%d (%.0f%%)", table_data$comorbidities$glaucoma$n[2], table_data$comorbidities$glaucoma$pct[2]),
      sprintf("%d (%.0f%%)", table_data$comorbidities$cataract$n[2], table_data$comorbidities$cataract$pct[2]),
      sprintf("%d (%.0f%%)", table_data$comorbidities$retina$n[2], table_data$comorbidities$retina$pct[2])
    ),
    Total = c(
      sprintf("%d (%.0f%%)", table_data$comorbidities$glaucoma$n[3], table_data$comorbidities$glaucoma$pct[3]),
      sprintf("%d (%.0f%%)", table_data$comorbidities$cataract$n[3], table_data$comorbidities$cataract$pct[3]),
      sprintf("%d (%.0f%%)", table_data$comorbidities$retina$n[3], table_data$comorbidities$retina$pct[3])
    )
  )
  knitr::kable(comorb_df, col.names = c("Condition", "Lapse in care", "No lapse in care", "Total"))

  cat("\n**Clinical Characteristics (Mean ± SD)**\n")
  clinical_df <- data.frame(
    Variable = c("Baseline Visual Acuity (logMAR)", 
                "Diabetes Complication Severity Index", 
                "Charlson Comorbidity Index"),
    Lapse = c(table_data$continuous$va$stat[1],
             table_data$continuous$dcsi$stat[1],
             table_data$continuous$cci$stat[1]),
    NoLapse = c(table_data$continuous$va$stat[2],
               table_data$continuous$dcsi$stat[2],
               table_data$continuous$cci$stat[2]),
    Total = c(table_data$continuous$va$stat[3],
             table_data$continuous$dcsi$stat[3],
             table_data$continuous$cci$stat[3])
  )
  knitr::kable(clinical_df, col.names = c("Variable", "Lapse in care", "No lapse in care", "Total"))
}

@@

  export_df <- rbind(export_df, data.frame(
    variable = "Total",
    lapse_value = lapse_total$n,
    lapse_prop = lapse_total$pct,
    lapse_sd = NA,
    no_lapse_value = no_lapse_total$n,
    no_lapse_prop = no_lapse_total$pct,
    no_lapse_sd = NA,
    total_value = total_total$n,
    total_prop = 100,
    total_sd = NA
  ))

@@

      export_df <- rbind(export_df, data.frame(
        variable = paste0("Sex_", level),
        lapse_value = lapse_val$n,
        lapse_prop = lapse_val$pct,
        lapse_sd = NA,
        no_lapse_value = no_lapse_val$n,
        no_lapse_prop = no_lapse_val$pct,
        no_lapse_sd = NA,
        total_value = total_val$n,
        total_prop = total_val$pct,
        total_sd = NA
      ))
    }
  }

@@

      export_df <- rbind(export_df, data.frame(
        variable = paste0("Age_", level),
        lapse_value = lapse_val$n,
        lapse_prop = lapse_val$pct,
        lapse_sd = NA,
        no_lapse_value = no_lapse_val$n,
        no_lapse_prop = no_lapse_val$pct,
        no_lapse_sd = NA,
        total_value = total_val$n,
        total_prop = total_val$pct,
        total_sd = NA
      ))
    }
  }

@@

      export_df <- rbind(export_df, data.frame(
        variable = paste0("Race_", level),
        lapse_value = lapse_val$n,
        lapse_prop = lapse_val$pct,
        lapse_sd = NA,
        no_lapse_value = no_lapse_val$n,
        no_lapse_prop = no_lapse_val$pct,
        no_lapse_sd = NA,
        total_value = total_val$n,
        total_prop = total_val$pct,
        total_sd = NA
      ))
    }
  }

@@

      export_df <- rbind(export_df, data.frame(
        variable = paste0("Insurance_", level),
        lapse_value = lapse_val$n,
        lapse_prop = lapse_val$pct,
        lapse_sd = NA,
        no_lapse_value = no_lapse_val$n,
        no_lapse_prop = no_lapse_val$pct,
        no_lapse_sd = NA,
        total_value = total_val$n,
        total_prop = total_val$pct,
        total_sd = NA
      ))
    }
  }

@@

  for (j in 1:length(treatment_names)) {
    if (!is.null(treatment_data[[j]])) {
      tx_data <- treatment_data[[j]]
      export_df <- rbind(export_df, data.frame(
        variable = treatment_names[j],
        lapse_value = tx_data$n[tx_data$lapse_group == "Lapse in care"],
        lapse_prop = tx_data$pct[tx_data$lapse_group == "Lapse in care"],
        lapse_sd = NA,
        no_lapse_value = tx_data$n[tx_data$lapse_group == "No lapse in care"],
        no_lapse_prop = tx_data$pct[tx_data$lapse_group == "No lapse in care"],
        no_lapse_sd = NA,
        total_value = tx_data$n[tx_data$lapse_group == "Total"],
        total_prop = tx_data$pct[tx_data$lapse_group == "Total"],
        total_sd = NA
      ))
    }
  }

@@

  for (j in 1:length(comorb_names)) {
    if (!is.null(comorb_data[[j]])) {
      com_data <- comorb_data[[j]]
      export_df <- rbind(export_df, data.frame(
        variable = comorb_names[j],
        lapse_value = com_data$n[com_data$lapse_group == "Lapse in care"],
        lapse_prop = com_data$pct[com_data$lapse_group == "Lapse in care"],
        lapse_sd = NA,
        no_lapse_value = com_data$n[com_data$lapse_group == "No lapse in care"],
        no_lapse_prop = com_data$pct[com_data$lapse_group == "No lapse in care"],
        no_lapse_sd = NA,
        total_value = com_data$n[com_data$lapse_group == "Total"],
        total_prop = com_data$pct[com_data$lapse_group == "Total"],
        total_sd = NA
      ))
    }
  }

@@

      export_df <- rbind(export_df, data.frame(
        variable = cv$name,
        lapse_value = lapse_stats$mean,
        lapse_prop = NA,
        lapse_sd = lapse_stats$sd,
        no_lapse_value = no_lapse_stats$mean,
        no_lapse_prop = NA,
        no_lapse_sd = no_lapse_stats$sd,
        total_value = total_stats$mean,
        total_prop = NA,
        total_sd = total_stats$sd
      ))
    }
  }

@@

```{r stratified-imputed}
# Function to process and average imputed datasets
create_imputed_stratified_table <- function(imputed_list) {

@@

  # Average totals
  avg_totals <- data.frame(
    Variable = "Total (averaged)",
    Lapse = paste0(round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(" .*", "", x$totals$Lapse))
    }))), " (", round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(".*\\((.*)%.*", "\\1", x$totals$Lapse))
    }))), "%)"),
    NoLapse = paste0(round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(" .*", "", x$totals$NoLapse))
    }))), " (", round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(".*\\((.*)%.*", "\\1", x$totals$NoLapse))
    }))), "%)"),
    Total = paste0(round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(" .*", "", x$totals$Total))
    }))), " (100%)")
  )

>>>>

    # Original
    orig_row <- original[original$variable == v, ]
    if (nrow(orig_row) > 0 && !is.na(orig_row$mean)) {
      table_df$Original[i] <- sprintf("%.4f (%.4f)", orig_row$mean, orig_row$sd)
    }

    # Submitted
    sub_row <- submitted[submitted$variable == v, ]
    if (nrow(sub_row) > 0 && !is.na(sub_row$mean)) {
      table_df$Submitted[i] <- sprintf("%.4f (%.4f)", sub_row$mean, sub_row$sd)
    }

    # Excluded
    exc_row <- excluded[excluded$variable == v, ]
    if (nrow(exc_row) > 0 && !is.na(exc_row$mean)) {
      table_df$Excluded[i] <- sprintf("%.4f (%.4f)", exc_row$mean, exc_row$sd)
    }

    # Imputed
    imp_row <- imputed[imputed$variable == v, ]
    if (nrow(imp_row) > 0 && !is.na(imp_row$mean)) {
      table_df$Imputed[i] <- sprintf("%.4f (%.4f)", imp_row$mean, imp_row$sd)
    }
  }

@@

    # Original
    orig_row <- original[original$variable_std == v, ]
    if (nrow(orig_row) > 0 && !is.na(orig_row$n)) {
      table_df$Original[i] <- sprintf("%.0f (%.4f%%)", orig_row$n, orig_row$pct)
    }

    # Submitted
    sub_row <- submitted[submitted$variable_std == v, ]
    if (nrow(sub_row) > 0 && !is.na(sub_row$n)) {
      table_df$Submitted[i] <- sprintf("%.0f (%.4f%%)", sub_row$n, sub_row$pct)
    }

    # Excluded
    exc_row <- excluded[excluded$variable_std == v, ]
    if (nrow(exc_row) > 0 && !is.na(exc_row$n)) {
      table_df$Excluded[i] <- sprintf("%.0f (%.4f%%)", exc_row$n, exc_row$pct)
    }

    # Imputed
    imp_row <- imputed[imputed$variable_std == v, ]
    if (nrow(imp_row) > 0 && !is.na(imp_row$n)) {
      table_df$Imputed[i] <- sprintf("%.1f (%.4f%%)", imp_row$n, imp_row$pct)
    }
  }

@@

# Display continuous variables
print(kable(continuous_table, 
      caption = "Continuous Variables: Mean (SD)",
      col.names = c("Variable", "Original", "Submitted", "Excluded", "Imputed (Average)")))

# Display categorical variables
print(kable(categorical_table,
      caption = "Categorical Variables: N (%)",
      col.names = c("Variable", "Original", "Submitted", "Excluded", "Imputed (Average)")))

@@

print(kable(sample_sizes, caption = "Sample Sizes"))
```

@@

```{r stratified-complete-cases, results='asis'}
# Use submitted_data for complete cases analysis
complete_cases_data <- submitted_data

@@

# Function to calculate stratified statistics
calculate_stratified_stats <- function(data, var, is_continuous = FALSE) {
  if (is_continuous) {
    # For continuous variables, calculate mean ± SD
    stats <- data |>
      group_by(lapse_group) |>
      summarise(
        mean = mean(!!sym(var), na.rm = TRUE),
        sd = sd(!!sym(var), na.rm = TRUE),
        .groups = "drop"
      ) |>
      mutate(
        stat = sprintf("%.4f ± %.4f", mean, sd)
      )

    # Add total
    total_stat <- data |>
      summarise(
        mean = mean(!!sym(var), na.rm = TRUE),
        sd = sd(!!sym(var), na.rm = TRUE)
      ) |>
      mutate(
        lapse_group = "Total",
        stat = sprintf("%.4f ± %.4f", mean, sd)
      )

@@

  } else {
    # For categorical variables
    # Calculate counts within each lapse group
    lapse_stats <- data |>
      filter(lapse_group == "Lapse in care") |>
      count(!!sym(var)) |>
      mutate(
        total_lapse = sum(n),
        pct = 100 * n / total_lapse,
        stat_lapse = sprintf("%d (%.4f%%)", n, pct)
      ) |>
      rename(level = !!sym(var))

    no_lapse_stats <- data |>
      filter(lapse_group == "No lapse in care") |>
      count(!!sym(var)) |>
      mutate(
        total_no_lapse = sum(n),
        pct = 100 * n / total_no_lapse,
        stat_no_lapse = sprintf("%d (%.4f%%)", n, pct)
      ) |>
      rename(level = !!sym(var))

    # Calculate total
    total_stats <- data |>
      count(!!sym(var)) |>
      mutate(
        total_all = sum(n),
        pct = 100 * n / total_all,
        stat_total = sprintf("%d (%.4f%%)", n, pct)
      ) |>
      rename(level = !!sym(var))

@@

  # Total row
  results$Total <- data.frame(
    Variable = "Total",
    Lapse = sprintf("%d (%.4f%%)", n_lapse, 100*n_lapse/n_total),
    NoLapse = sprintf("%d (%.4f%%)", n_no_lapse, 100*n_no_lapse/n_total),
    Total = sprintf("%d (100%%)", n_total),
    stringsAsFactors = FALSE
  )

@@

  # Display totals
  cat("**Total Patients**\n")
  print(knitr::kable(table_data$totals))

@@

  cat("\n*Sex*\n")
  print(knitr::kable(table_data$sex))

  cat("\n*Age (years)*\n")
  print(knitr::kable(table_data$age))

  cat("\n*Race/Ethnicity*\n")
  print(knitr::kable(table_data$race))

  cat("\n*Insurance*\n")
  print(knitr::kable(table_data$insurance))

@@

  cat("\n*Severity of DR*\n")
  print(knitr::kable(table_data$dr))

  cat("\n*DR Treatments (% with treatment)*\n")
  treatments_df <- data.frame(
    Treatment = c("PRP", "Focal laser", "Anti-VEGF", "Other injections"),
    Lapse = c(
      sprintf("%d (%.4f%%)", table_data$treatments$prp$n[1], table_data$treatments$prp$pct[1]),
      sprintf("%d (%.4f%%)", table_data$treatments$focal$n[1], table_data$treatments$focal$pct[1]),
      sprintf("%d (%.4f%%)", table_data$treatments$vegf$n[1], table_data$treatments$vegf$pct[1]),
      sprintf("%d (%.4f%%)", table_data$treatments$other$n[1], table_data$treatments$other$pct[1])
    ),
    NoLapse = c(
      sprintf("%d (%.4f%%)", table_data$treatments$prp$n[2], table_data$treatments$prp$pct[2]),
      sprintf("%d (%.4f%%)", table_data$treatments$focal$n[2], table_data$treatments$focal$pct[2]),
      sprintf("%d (%.4f%%)", table_data$treatments$vegf$n[2], table_data$treatments$vegf$pct[2]),
      sprintf("%d (%.4f%%)", table_data$treatments$other$n[2], table_data$treatments$other$pct[2])
    ),
    Total = c(
      sprintf("%d (%.4f%%)", table_data$treatments$prp$n[3], table_data$treatments$prp$pct[3]),
      sprintf("%d (%.4f%%)", table_data$treatments$focal$n[3], table_data$treatments$focal$pct[3]),
      sprintf("%d (%.4f%%)", table_data$treatments$vegf$n[3], table_data$treatments$vegf$pct[3]),
      sprintf("%d (%.4f%%)", table_data$treatments$other$n[3], table_data$treatments$other$pct[3])
    )
  )
  print(knitr::kable(treatments_df, col.names = c("Treatment", "Lapse in care", "No lapse in care", "Total")))

  cat("\n*Ophthalmologic Comorbidities*\n")
  comorb_df <- data.frame(
    Condition = c("Glaucoma", "Prior cataract surgery", "Other retinal disease"),
    Lapse = c(
      sprintf("%d (%.4f%%)", table_data$comorbidities$glaucoma$n[1], table_data$comorbidities$glaucoma$pct[1]),
      sprintf("%d (%.4f%%)", table_data$comorbidities$cataract$n[1], table_data$comorbidities$cataract$pct[1]),
      sprintf("%d (%.4f%%)", table_data$comorbidities$retina$n[1], table_data$comorbidities$retina$pct[1])
    ),
    NoLapse = c(
      sprintf("%d (%.4f%%)", table_data$comorbidities$glaucoma$n[2], table_data$comorbidities$glaucoma$pct[2]),
      sprintf("%d (%.4f%%)", table_data$comorbidities$cataract$n[2], table_data$comorbidities$cataract$pct[2]),
      sprintf("%d (%.4f%%)", table_data$comorbidities$retina$n[2], table_data$comorbidities$retina$pct[2])
    ),
    Total = c(
      sprintf("%d (%.4f%%)", table_data$comorbidities$glaucoma$n[3], table_data$comorbidities$glaucoma$pct[3]),
      sprintf("%d (%.4f%%)", table_data$comorbidities$cataract$n[3], table_data$comorbidities$cataract$pct[3]),
      sprintf("%d (%.4f%%)", table_data$comorbidities$retina$n[3], table_data$comorbidities$retina$pct[3])
    )
  )
  print(knitr::kable(comorb_df, col.names = c("Condition", "Lapse in care", "No lapse in care", "Total")))

  cat("\n**Clinical Characteristics (Mean ± SD)**\n")
  clinical_df <- data.frame(
    Variable = c("Baseline Visual Acuity (logMAR)", 
                "Diabetes Complication Severity Index", 
                "Charlson Comorbidity Index"),
    Lapse = c(table_data$continuous$va$stat[1],
             table_data$continuous$dcsi$stat[1],
             table_data$continuous$cci$stat[1]),
    NoLapse = c(table_data$continuous$va$stat[2],
               table_data$continuous$dcsi$stat[2],
               table_data$continuous$cci$stat[2]),
    Total = c(table_data$continuous$va$stat[3],
             table_data$continuous$dcsi$stat[3],
             table_data$continuous$cci$stat[3])
  )
  print(knitr::kable(clinical_df, col.names = c("Variable", "Lapse in care", "No lapse in care", "Total")))
}

@@

  export_df <- rbind(export_df, data.frame(
    variable = "Total",
    lapse_value = lapse_total$n,
    lapse_prop = round(lapse_total$pct, 4),
    lapse_sd = NA,
    no_lapse_value = no_lapse_total$n,
    no_lapse_prop = round(no_lapse_total$pct, 4),
    no_lapse_sd = NA,
    total_value = total_total$n,
    total_prop = 100,
    total_sd = NA
  ))

@@

      export_df <- rbind(export_df, data.frame(
        variable = paste0("Sex_", level),
        lapse_value = lapse_val$n,
        lapse_prop = round(lapse_val$pct, 4),
        lapse_sd = NA,
        no_lapse_value = no_lapse_val$n,
        no_lapse_prop = round(no_lapse_val$pct, 4),
        no_lapse_sd = NA,
        total_value = total_val$n,
        total_prop = round(total_val$pct, 4),
        total_sd = NA
      ))
    }
  }

@@

      export_df <- rbind(export_df, data.frame(
        variable = paste0("Age_", level),
        lapse_value = lapse_val$n,
        lapse_prop = round(lapse_val$pct, 4),
        lapse_sd = NA,
        no_lapse_value = no_lapse_val$n,
        no_lapse_prop = round(no_lapse_val$pct, 4),
        no_lapse_sd = NA,
        total_value = total_val$n,
        total_prop = round(total_val$pct, 4),
        total_sd = NA
      ))
    }
  }

@@

      export_df <- rbind(export_df, data.frame(
        variable = paste0("Race_", level),
        lapse_value = lapse_val$n,
        lapse_prop = round(lapse_val$pct, 4),
        lapse_sd = NA,
        no_lapse_value = no_lapse_val$n,
        no_lapse_prop = round(no_lapse_val$pct, 4),
        no_lapse_sd = NA,
        total_value = total_val$n,
        total_prop = round(total_val$pct, 4),
        total_sd = NA
      ))
    }
  }

@@

      export_df <- rbind(export_df, data.frame(
        variable = paste0("Insurance_", level),
        lapse_value = lapse_val$n,
        lapse_prop = round(lapse_val$pct, 4),
        lapse_sd = NA,
        no_lapse_value = no_lapse_val$n,
        no_lapse_prop = round(no_lapse_val$pct, 4),
        no_lapse_sd = NA,
        total_value = total_val$n,
        total_prop = round(total_val$pct, 4),
        total_sd = NA
      ))
    }
  }

@@

  for (j in 1:length(treatment_names)) {
    if (!is.null(treatment_data[[j]])) {
      tx_data <- treatment_data[[j]]
      export_df <- rbind(export_df, data.frame(
        variable = treatment_names[j],
        lapse_value = tx_data$n[tx_data$lapse_group == "Lapse in care"],
        lapse_prop = round(tx_data$pct[tx_data$lapse_group == "Lapse in care"], 4),
        lapse_sd = NA,
        no_lapse_value = tx_data$n[tx_data$lapse_group == "No lapse in care"],
        no_lapse_prop = round(tx_data$pct[tx_data$lapse_group == "No lapse in care"], 4),
        no_lapse_sd = NA,
        total_value = tx_data$n[tx_data$lapse_group == "Total"],
        total_prop = round(tx_data$pct[tx_data$lapse_group == "Total"], 4),
        total_sd = NA
      ))
    }
  }

@@

  for (j in 1:length(comorb_names)) {
    if (!is.null(comorb_data[[j]])) {
      com_data <- comorb_data[[j]]
      export_df <- rbind(export_df, data.frame(
        variable = comorb_names[j],
        lapse_value = com_data$n[com_data$lapse_group == "Lapse in care"],
        lapse_prop = round(com_data$pct[com_data$lapse_group == "Lapse in care"], 4),
        lapse_sd = NA,
        no_lapse_value = com_data$n[com_data$lapse_group == "No lapse in care"],
        no_lapse_prop = round(com_data$pct[com_data$lapse_group == "No lapse in care"], 4),
        no_lapse_sd = NA,
        total_value = com_data$n[com_data$lapse_group == "Total"],
        total_prop = round(com_data$pct[com_data$lapse_group == "Total"], 4),
        total_sd = NA
      ))
    }
  }

@@

      export_df <- rbind(export_df, data.frame(
        variable = cv$name,
        lapse_value = ifelse(is.na(lapse_stats$mean), NA, round(lapse_stats$mean, 4)),
        lapse_prop = NA,
        lapse_sd = ifelse(is.na(lapse_stats$sd), NA, round(lapse_stats$sd, 4)),
        no_lapse_value = ifelse(is.na(no_lapse_stats$mean), NA, round(no_lapse_stats$mean, 4)),
        no_lapse_prop = NA,
        no_lapse_sd = ifelse(is.na(no_lapse_stats$sd), NA, round(no_lapse_stats$sd, 4)),
        total_value = ifelse(is.na(total_stats$mean), NA, round(total_stats$mean, 4)),
        total_prop = NA,
        total_sd = ifelse(is.na(total_stats$sd), NA, round(total_stats$sd, 4))
      ))
    }
  }

@@

```{r stratified-imputed, results='asis'}
# Function to process and average imputed datasets
create_imputed_stratified_table <- function(imputed_list) {

@@

  # Average totals
  avg_totals <- data.frame(
    Variable = "Total (averaged)",
    Lapse = paste0(round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(" .*", "", x$totals$Lapse))
    })), 4), " (", round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(".*\\((.*)%.*", "\\1", x$totals$Lapse))
    })), 4), "%)"),
    NoLapse = paste0(round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(" .*", "", x$totals$NoLapse))
    })), 4), " (", round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(".*\\((.*)%.*", "\\1", x$totals$NoLapse))
    })), 4), "%)"),
    Total = paste0(round(mean(sapply(all_results, function(x) {
      as.numeric(gsub(" .*", "", x$totals$Total))
    })), 4), " (100%)")
  )
